{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed, Object Tracking

### 2017-06-16 bmvc_review.tex
Some More Cleaning

{\it Burak: Remove LCT part!}

We also compare the proposed {\it E}nKCF tracker to the LCT
\cite{ma2015long} tracker in table~\ref{table:Comparison_to_LCT}.  By
using three KCFs ( $R_{t}^{L}$, $R_{t}^{S}$, $R_{s}$) in {\it E}nKCF,
we can achieve higher accuracy than using $R_{s}$ and $R_{t}^{L}$ or
$R_{t}^{S}$ with similar run-time performance. On the other hand, we
employ $R_{s}$ and $R_{t}^{L}$ or $R_{t}^{S}$ in the LCT framework as
we run filters in every frame. Running another filter, $R_{t}^{L}$ or
$R_{t}^{S}$, in the {\it E}nKCF framework not only gives us
significantly higher run-time performance but also higher
accuracy. Finally, we modify the LCT tracker ({\it m}LCT) and run
$R_{t}^{L}$, $R_{t}^{S}$, and $R_{s}$ in every frame in the given
order. $R_{t}^{S}$ uses the translation estimation given by
$R_{t}^{L}$ to update translation and $R_{s}$ uses the final
translation estimation given by $R_{t}^{S}$ to update
scale. Interestingly, running two complementary translation filter
results in significant improvement at the cost of decreased run-time
performance. In conclusion, running two complementary translation
filter and a scale filter in the {\it E}nKCF framework not only
provides high speed but also more accurate tracker than the baseline
methods having one translation and one scale filter.
\begin{table}[!h]
\smaller
\begin{center}
\color{green}--- Best \hspace{.15\linewidth}\color{red}--- $2^{nd}$ Best \hspace{.15\linewidth}\color{blue}--- $3^{th}$ Best \color{black}\\
\resizebox{\textwidth}{!}{\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
\hline
Method & {\it E}nKCF & $R_{t}^{S}$+$R_{t}^{L}$+$R_{s}$ & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & $R_{t}^{L}$* & $R_{t}^{S}$* & $R_{t}^{L}$+$R_{s}$* & $R_{t}^{S}$+$R_{s}$* & $R_{t}^{L}+R_{t}^{S}$+$R_{s}$* \\
\hline\hline
Pr. ($20$px) & \color{blue}53.9 & 48.93 &52.41 & 48.10 & 51.88 & 51.29 & \color{red} 55.85 & 52.14 & \color{green}58.16 \\
SR ($50\%$) & \color{red} 40.2 & 36.75 & 38.23 & 36.04 & 35.12 & 34.43 & \color{blue}39.89 & 38.51 & \color{green}41.58 \\
FPS & \color{red} 416 & \color{blue}412 & 370 & \color{green}425 & 365 & 384 & 135 & 151 & 99 \\
\hline
\end{tabular}}
\end{center}
\caption{Evaluations of the different combinations of the proposed
  KCFs in UAV123 dataset. The $2^{nd}$ method swaps the order of
  $R_{t}^{L}$ and $R_{t}^{S}$ (fig.~\ref{Workflows}). The $3^{th}$
  method removes $R_{t}^{S}$ and replaces with $R_{t}^{L}$ whereas the
  $3^{th}$ one removes $R_{t}^{L}$. The methods denoted with "*" run
  the filters in every frame in the listed order. The LCT tracker
  \cite{ma2015long} runs a translation and scale filter in every frame
  (similar to $6^{th}$ method) and couples a re-detection method to
  perform long-term tracking at $\approx30$ fps.}
\label{table:Comparison_to_LCT}
\end{table}

>>>>

We also evaluate the performances of the different combinations of the
proposed correlation filters and compare them to the {\it E}nKCF as shown in table~\ref{table:Comparison_to_LCT}.  
By using three KCFs ( $R_{t}^{L}$, $R_{t}^{S}$, $R_{s}$) in {\it E}nKCF,
we can achieve higher accuracy than using $R_{s}$ and $R_{t}^{L}$ or
$R_{t}^{S}$ with similar run-time performance. On the other hand, we
employ $R_{s}$ and $R_{t}^{L}$ or $R_{t}^{S}$ and run them in every frame in a similar way
to the multiple correlation filter framework of the LCT tracker \cite{ma2015long}. Running another filter, $R_{t}^{L}$ or
$R_{t}^{S}$, in the {\it E}nKCF framework not only boosts run-time performance but also increases
accuracy. Finally, we run  $R_{L}$, $R_{t}^{S}$ and $R_{s}$ in every frame in the in the given order. 
$R_{t}^{S}$ uses the translation estimation given by
$R_{t}^{L}$ to update translation and finally $R_{s}$ uses the final
translation estimation given by $R_{t}^{S}$ to update the
scale. Interestingly, running two complementary translation filter
results in significant improvement at the cost of decreased run-time
performance. In conclusion, running two complementary translation
filter and a scale filter in the {\it E}nKCF framework not only
provides high speed but also more accurate tracker than the baseline
methods having one translation and one scale filter.
\begin{table}[!h]
\smaller
\begin{center}
\color{green}--- Best \hspace{.15\linewidth}\color{red}--- $2^{nd}$ Best \hspace{.15\linewidth}\color{blue}--- $3^{th}$ Best \color{black}\\
\resizebox{\textwidth}{!}{\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
\hline
Method & {\it E}nKCF & $R_{t}^{S}$+$R_{t}^{L}$+$R_{s}$ & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & $R_{t}^{L}$* & $R_{t}^{S}$* & $R_{t}^{L}$+$R_{s}$* & $R_{t}^{S}$+$R_{s}$* & $R_{t}^{L}+R_{t}^{S}$+$R_{s}$* \\
\hline\hline
Pr. ($20$px) & \color{blue}53.9 & 48.93 &52.41 & 48.10 & 51.88 & 51.29 & \color{red} 55.85 & 52.14 & \color{green}58.16 \\
SR ($50\%$) & \color{red} 40.2 & 36.75 & 38.23 & 36.04 & 35.12 & 34.43 & \color{blue}39.89 & 38.51 & \color{green}41.58 \\
FPS & \color{red} 416 & \color{blue}412 & 370 & \color{green}425 & 365 & 384 & 135 & 151 & 99 \\
\hline
\end{tabular}}
\end{center}
\caption{Evaluations of the different combinations of the proposed
  KCFs in UAV123 dataset. The $2^{nd}$ method swaps the order of
  $R_{t}^{L}$ and $R_{t}^{S}$ (fig.~\ref{Workflows}). The $3^{th}$
  method removes $R_{t}^{S}$ and replaces with $R_{t}^{L}$ whereas the
  $3^{th}$ one removes $R_{t}^{L}$. The methods denoted with "*" run
  the filters in every frame in the listed order. The LCT tracker
  \cite{ma2015long} runs a translation and scale filter in every frame
  (similar to $6^{th}$ method) and couples a re-detection method to
  perform long-term tracking at $\approx30$ fps.}
\label{table:Comparison_to_LCT}
\end{table}
